Health Data

### 2019-12-09 01_health_data.Rmd
Add mental health indicator to dataset

```{r cdc500}
cdc_urls <- list(
  "physact" = "https://chronicdata.cdc.gov/resource/axqz-rkkp.json?stateabbr=NY",
  "obesity" = "https://chronicdata.cdc.gov/resource/bjvu-3y7d.json?stateabbr=NY"
)

>>>>

```{r cdc500}
cdc_urls <- list(
  "physact" = "https://chronicdata.cdc.gov/resource/axqz-rkkp.json?stateabbr=NY",
  "obesity" = "https://chronicdata.cdc.gov/resource/bjvu-3y7d.json?stateabbr=NY",
  "mhealth" = "https://chronicdata.cdc.gov/resource/i2ek-k3pa.json?stateabbr=NY"
)
